---
title: "World Values Survey data"
author: "Vinita Vader"
date: "27th January 2021"
output:
  html_document:
    toc: yes
editor_options: 
  chunk_output_type: console
  
---


```{r setup, include=FALSE}
options(Encoding="UTF-8")
knitr::opts_chunk$set(echo = FALSE,
                      warnings = FALSE,
                      message = FALSE,
                      errors = TRUE,
                      eval = TRUE,
                      fig.width = 8, fig.height = 7)

library(tidyverse) #data wrangling
library(dplyr)
library(rio) #data import
library(here) #call data
library(janitor) #clean data col names
library(stringr) #
library(forcats) #
library(ggplot2) #plotting data
library(esvis) #effect size
library(kableExtra) #print pretty tables
library(papaja) #in line code
here() #look at the path
library(leaflet)
remotes::install_github("emlaet/wwmetrics")
library(wwmetrics)
cd = data("CultDist")
View(cd)
devtools::install_github("tidyverse/googledrive")
library(googledrive)

dl <- drive_download(
  "World_Values_Survey_Wave_7_Inverted_R_v1_5.rdata")


options(tibble.print_max = 10) #print first 50 rows
```


# Data import and clean

```{r data_cleaning,include=TRUE, echo=TRUE, eval=TRUE}
raw.data = import(here("data", "World_Values_Survey_Wave_7_Inverted_R_v1_5.rdata"), setclass = "tb_df") %>% 
  characterize() %>% 
  clean_names()

#use this code when forking
dl = drive_download(
  "World_Values_Survey_Wave_7_Inverted_R_v1_5.rdata")

raw.data = import("World_Values_Survey_Wave_7_Inverted_R_v1_5.rdata", setclass = "tb_df") %>% 
  characterize() %>% 
  clean_names()

#names(raw.data)
#View(raw.data)


#renaming, recoding levels in the data for required variables
clean.data = raw.data %>% 
  #step 1 = select variables to be used
  select(b_country_alpha, q106, q107, q108, q109, q111, q289cs9, q262, q152, q170p, q173p, q169p, q238p, q21p, o1_longitude, o2_latitude, q260) %>% #q260 - gender
  #step 2 = rename variables being used
  mutate(country = factor(b_country_alpha), 
         rel.denom = factor(q289cs9)) %>% 
  #drop those NAs, no missing values
  drop_na() %>% 
  #reverse coding
  mutate(q107r = 11 - q107,
         q109r = 11 - q109) %>% 
  #recode levels to something you understand
  mutate(rel.denom = recode(rel.denom,
`-5`= "Other missing",
`-4`="Not asked",
`-2`="No answer",
`-1`="Dont know",
`10000000` = "Catholic, not further defined",
`10100000` = "Roman Catholic",
`10203000` = "Latin Church",
`10205010` = "Byzantine Rite",
`20000000` = "Maronite Church",
`20200000` = "Protestant, not further defined",
`20206022` = "Lutheran, not further defined",
`20222370` = "Protestant Free Church of Germany",
`20302000` = "Evangelical Lutheran Church in Russia, Ukraine, Kazakhstan",
`20400000` = "Presbyterianism",
`20600000` = "Anglican, not further defined",
`20636010` = "Baptist, not further defined",
`20700000` = "Evangelical Baptist Union of Ukraine",
`20720060` = "Methodist, not further defined",
`20804000` = "The Salvation Army",
`20805000` = "Adventist movement (Sunday observing)",
`20805020` = "Adventist movement (Seventh Day Sabbath/Saturday observing) Seventh-day Adventist Church",
`21000000` = "Plymouth Brethren, not further defined",
`21101010` = "New Apostolic Church",
`21200000` = "Pentecostal and Charismatic, not further defined",
`21212050` = "Australian Christian Church (Asemblies of God)",
`21218000` = "Celestial Church of Christ",
`21226000` = "Church of the Foursquare Gospel",
`21283005` = "Churches of Christ in Australia",
`21285030` = "Born Again Movement",
`21319000` = "United Church of Christ in the Philippines",
`21320000` = "Uniting Church in Australia",
`21321050` = "United Evangelical Church in Nigeria",
`21401250` = "Assembly of God",
`21603100` = "Brotherhood of the Cross and Star",
`21621100` = "Protestant Churches without free churches (Germany)",
`30100000` = "Eastern Orthodox, not further defined",
`30106000` = "Russian Orthodox Church",
`30108000` = "Serbian Orthodox Church",
`30111000` = "Cypriot Orthodox Church",
`30112000` = "Orthodox Church of Greece",
`30117000` = "Orthodox Church of Ukraine",
`30202001` = "Armenian Apostolic Church",
`30202009` = "Ethiopian Orthodox Tewahedo Church",
`40000000` = "Judaism",
`50000000` = "Islam, not further defined",
`50101000` = "Sunni",
`50202000` = "Shia",
`50302000` = "Ibadi",
`50500010` = "Druze",
`50500060` = "Bahai Faith",
`50500080` = "Second Advent; Parousia",
`60000000` = "Hindu",
`70000000` = "Buddhist",
`70200000` = "Hoahaoism",
`80000000` = "Other Christian, not further defined",
`80213100` = "American Israelism and Latter Day Saint movement",
`80213122` = "Mormons",
`80213139` = "World Missionary Movement",
`80213304` = "Jehovah's Witnesses",
`80213401` = "La Luz del Mundo",
`80213501` = "Iglesia ni Cristo (Church of Christ)",
`80213502` = "Members Church of God International",
`80217003` = "Church of God (Seventh-Day)",
`80400035` = "Evangelicalism",
`80400037` = "Gnosticism",
`80502002` = "Cao Đài",
`80502010` = "Santeria",
`90000000` = "Other; nfd",
`90101000` = "Taoism (Han Chinese)",
`90102000` = "Confucianists",
`90103000` = "Yiguandao",
`90104000` = "Xuanyuan jiao",
`90105000` = "Cihui Tang",
`90200000` = "Ethnic religions excluding some in separate categories",
`90201115` = "Wicca-Pagan` Witchcraft",
`90202120` = "Mandaeism",
`90300000` = "African traditional religions",
`90400000` = "Sikhism",
`90500000` = "Spiritism",
`90800000` = "Neo-paganism",
`100000020`= "Noneligious",
`100000030`= "Agnostic",
`100000040`= "Atheist"), 
country = recode(b_country_alpha,
              "AND" = "Andorra",
              "ARG" = "Argentina", 
              "AUS" = "Australia", 
              "BGD" = "Bangladesh", 
              "BOL" = "Bolivia", 
              "BRA" = "Brazil", 
              "CHL" = "Chile", 
              "CHN" = "China", 
              "COL" = "Colombia", 
              "CYP" = "Cyprus", 
              "ECU" = "Ecuador", 
              "EGY" = "Egypt", 
              "ETH" = "Ethipoia",
              "DEU" = "Germany",
              "GRC" = "Greece", 
              "GTM" = "Guatemala", 
              "HKG" = "Hong Kong SAR", 
              "IDN" = "Indonesia", 
              "IRN" ="Iran", 
              "IRQ" = "Iraq", 
              "JPN" = "Japan", 
              "JOR" = "Jordan", 
              "KAZ" = "Kazakhstan", 
              "KGZ" = "Kyrgyzstan", 
              "LBN" = "Lebanon",
              "MAC" = "Macau.SAR", 
              "MYS" = "Malaysia",
              "MEX" = "Mexico", 
              "MMR" = "Myanmar", 
              "NZL" = "New Zealand", 
              "NIC" = "Nicargua", 
              "NGA" = "Nigeria", 
              "PAK" = "Pakistan", 
              "PER" = "Peru", 
              "PHL" = "Philippines", 
              "PRI" = "Puerto.Rico", 
              "ROU" = "Romania", 
              "RUS" = "Russia", 
              "SRB" = "Serbia", 
              "KOR" = "South.Korea", 
              "TWN" = "Taiwan ROC", 
              "TJK" = "Tajikistan", 
              "THA" = "Thailand", 
              "TUN" = "Tunisia", 
              "TUR" = "Turkey", 
              "UKR" = "Ukraine", 
              "USA" = "United States", 
              "VNM" = "Vietnam",
              "ZWE" = "Zimbabwe")) 


#Countries included in this dataset
clean.data %>% 
  select(country) %>% 
  group_by(country) %>% 
  count() %>% 
  rownames_to_column() %>% 
   kbl() %>%
   kable_styling(fixed_thead = T) 


country_coord = clean.data %>% 
  select(country, o1_longitude, o2_latitude) %>%
  group_by(country) %>% 
  summarise(mean_long = mean(o1_longitude),
         mean_lat = mean(o2_latitude))
  

  
```

# Data information

I am using the [7th wave of the World Values Survey data](https://www.worldvaluessurvey.org/WVSDocumentationWV7.jsp) for this project. It is a large dataset consisting of 48 countries and a sample size of `r printnum(nrow(data))`. I intend to look at countrywise differences across indices/individual items in the questionnaire. It includes items measuring social values, attitudes, political and cultural regimes, postmaterialism to name a few. Following are some examples of codes which I intend to explore in order to understand cross ciuntry differences. 

# Examples of description plots 
## Defense
   - "defense is important"
```{r include=TRUE, echo=TRUE, eval=TRUE}

df1 = clean.data %>% 
  select(country, q152) %>%
  group_by(country, q152) %>% 
  count() %>% 
  pivot_wider(names_from = "q152", values_from = n) %>% 
  mutate(`4` = replace_na(`4`, 0)) %>% #replace the pesky NA with 0
  mutate(total.n = sum(`1`, `2`, `3`, `4`)) %>% 
  pivot_longer(cols = c(`1`, `2`, `3`, `4`), names_to = "q152", values_to = "importance") %>% 
  mutate("perc.imp" = (importance/total.n)*100) %>% 
  filter(q152 == "2") %>% #defense is important
  arrange(desc(perc.imp)) %>% 
  data.frame()%>%
  as_tibble() %>% 
  arrange(desc(perc.imp))

df1.map = left_join(country_coord, df1, "country")

library(leaflet)
map = leaflet(df1.map)
# View(df1.map)


#circles with color gradient
colors = c("grey", "blue")
pal = colorFactor(colors, df1.map$perc.imp)
leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(data = df1.map, lat = ~mean_lat, lng = ~mean_long, radius = ~2, color = ~pal(perc.imp))

leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = df1.map)

pal <- colorNumeric(
  palette = "Blues",
  domain = df1.map$perc.imp)

map %>% 
  addPolygons()

map %>% 
    addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,  lng = mean_long,
  lat = mean_lat,
    color = ~pal(perc.imp))

# color of the country 
# Create a continuous palette function
pal <- colorNumeric(
  palette = "Blues",
  domain = df1.map$perc.imp)

# Apply the function to provide RGB colors to addPolygons
library(rgdal)
countries = readOGR("https://raw.githubusercontent.com/datasets/geo-boundaries-world-110m/master/countries.geojson")

countries = (readOGR(here("data", "world.geojson")))
View(countries)

map <- leaflet(countries)


pal <- colorNumeric(
  palette = "Blues",
  domain = countries$gdp_md_est)

map %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~pal(gdp_md_est))
?addPolygons
df1 %>% 
 kbl() %>%
 kable_styling(fixed_thead = T)

df1 %>% 
  select(country, perc.imp) %>%
  mutate(perc.imp = as.integer(perc.imp)) %>% 
  ggplot(aes(x = fct_reorder(country, perc.imp), y = perc.imp))+
   geom_bar(stat = "identity", fill = "cornflowerblue") +
   coord_flip() +
   theme_minimal()
  
```

## Religious pride
   - "The only acceptable religion is my religion"
```{r include=TRUE, echo=TRUE, eval=FALSE}
clean.data %>% 
  select(country, q170p) %>%
  group_by(country, q170p) %>% 
  count() %>% 
  pivot_wider(names_from = "q170p", values_from = n) %>% 
  mutate(total.n = sum(`1`, `2`, `3`, `4`)) %>% 
  pivot_longer(cols = c(`1`, `2`, `3`, `4`), names_to = "q170p", values_to = "agreement") %>% 
  mutate("perc.agree" = (agreement/total.n)*100) %>% 
  filter(q170p == "1") %>% #1 = strongly agree
  arrange(desc(perc.agree)) %>% 
  data.frame()%>% 
  dplyr::slice_head(n = 10)
```

## Religiousness
   - "Independently of whether you attend religious services or not, would you say you are...?"
```{r include=TRUE, echo=TRUE, eval=FALSE}   
clean.data %>% 
  select(country, q173p) %>%
  group_by(country, q173p) %>% 
  count() %>% 
  pivot_wider(names_from = "q173p", values_from = n) %>% 
  mutate(`1` = replace_na(`1`, 0)) %>% #replace the pesky NA with 0
  mutate(total.n = sum(`1`, `2`, `3`)) %>% 
  pivot_longer(cols = c(`1`, `2`, `3`), names_to = "q173p", values_to = "religious") %>% 
  mutate("perc.religious" = (religious/total.n)*100) %>% 
  filter(q173p == "1") %>% #1 = religious
  arrange(desc(perc.religious)) %>% 
  data.frame()%>% 
  dplyr::slice_head(n = 10)
```  

## Religiousness
   - "Whenever science and religion conflict, religion is always right"
```{r include=TRUE, echo=TRUE, eval=FALSE}   
clean.data %>% 
  select(country, q169p) %>%
  group_by(country, q169p) %>% 
  count() %>% 
  pivot_wider(names_from = "q169p", values_from = n) %>% 
  mutate(`1` = replace_na(`1`, 0)) %>% #replace the pesky NA with 0
  mutate(total.n = sum(`1`, `2`, `3`)) %>% 
  pivot_longer(cols = c(`1`, `2`, `3`), names_to = "q169p", values_to = "rel.right") %>% 
  mutate("perc_rel.right" = (rel.right/total.n)*100) %>% 
  filter(q169p == "1") %>% #1 = strongly agree that - Whenever science and religion conflict, religion is always right
  arrange(desc(perc_rel.right)) %>% 
  data.frame()%>% 
  dplyr::slice_head(n = 10)
```

## Democratic orientation
   - "Having a democratic political system"
```{r include=TRUE, echo=TRUE, eval=FALSE}   

clean.data %>% 
  select(country, q238p) %>%
  group_by(country, q238p) %>% 
  count() %>% 
  pivot_wider(names_from = "q238p", values_from = n) %>% 
  mutate(total.n = sum(`1`, `2`, `3`, `4`)) %>% 
  pivot_longer(cols = c(`1`, `2`, `3`, `4`), names_to = "q238p", values_to = "non.democratic") %>% 
  mutate("perc_non.democratic" = (non.democratic/total.n)*100) %>% 
  filter(q238p == "4") %>% #1 = Very bad - Having a democratic political system
  arrange(desc(perc_non.democratic)) %>% 
  data.frame()%>% 
  dplyr::slice_head(n = 10)
```

## Immigrants
   - "not have as neighbors"
```{r include=TRUE, echo=TRUE, eval=FALSE}   
  
clean.data %>% 
  select(country, q21p) %>%
  group_by(country, q21p) %>% 
  count() %>% 
  pivot_wider(names_from = "q21p", values_from = n) %>% 
  mutate(total.n = sum(`1`, `0`)) %>% 
  pivot_longer(cols = c(`1`, `0`), names_to = "q21p", values_to = "immigrants") %>% 
  mutate("perc_immigrants" = (immigrants/total.n)*100) %>% 
  filter(q21p == "1") %>% #1 = not have as neighbors
  arrange(desc(perc_immigrants)) %>% 
  data.frame()
#%>% 
  dplyr::slice_head(n = 10)
  


```

## Economic Values
```{r include=TRUE, echo=TRUE, eval=FALSE}

capitalism.d = clean.data %>%
  filter(q111 %in% c("1", "2")) %>% 
  rowwise() %>% 
  mutate(capitalism = sum(q106, q107r, q108, q109r, q111)) %>%
  mutate(capitalism = as.integer(capitalism)) %>%
  select(country, capitalism, rel.denom, q262) %>% 
  data_frame()

  
cd = coh_d(capitalism.d, capitalism~country) #compute effect sizes for all country pairs

# ANDORRA
cd %>% 
  filter(country_ref == "Andorra") %>% 
  mutate(highlight = ifelse(country_foc == 'Chile', T, F)) %>%
  select(country_foc, coh_d, highlight) %>% 
  ggplot(aes(x = fct_reorder(country_foc, abs(coh_d)), y = coh_d, fill = highlight)) +
        geom_bar(stat = "identity", aes(fill = highlight), alpha = .8)+ 
  scale_fill_manual(values = c("cornflowerblue", rep("coral1", 46)))+
  theme_minimal(base_size = 8)+
        coord_flip() +  
        labs(x = "Countries",
             y = "Cohen's d",
             title = "Distance from Andorra")+
  guides(fill=FALSE)
  

# Bangladesh
cd %>% 
  filter(country_ref == "Bangladesh") %>% 
  mutate(highlight = ifelse(country_foc == 'Vietnam', T, F)) %>%
  select(country_foc, coh_d, highlight) %>% 
  ggplot(aes(x = fct_reorder(country_foc, abs(coh_d)), y = coh_d, fill = highlight)) +
        geom_bar(stat = "identity", aes(fill = highlight), alpha = .8)+ 
  scale_fill_manual(values = c("cornflowerblue", rep("coral1", 46)))+
  theme_minimal(base_size = 8)+
        coord_flip() +  
        labs(x = "Countries",
             y = "Cohen's d",
             title = "Distance from Bangladesh")+
  guides(fill=FALSE)

# USA
cd %>% 
  filter(country_ref == "United States") %>% 
  mutate(highlight = ifelse(country_foc == 'Chile', T, F)) %>%
  select(country_foc, coh_d, highlight) %>% 
  ggplot(aes(x = fct_reorder(country_foc, abs(coh_d)), y = coh_d, fill = highlight)) +
        geom_bar(stat = "identity", aes(fill = highlight), alpha = .8)+ 
  scale_fill_manual(values = c("cornflowerblue", rep("coral1", 46)))+
  theme_minimal(base_size = 8)+
        coord_flip() +  
        labs(x = "Countries",
             y = "Cohen's d",
             title = "Distance from USA")+
  guides(fill=FALSE)

#Countries with GDP growth greater than 5% in 2017
# Bangladesh, Malaysia, Vietnam, Myanmar, Indonesia, China, Phillipines, Tajikistan, Macau.SAR, Romania, Pakistan, Ethiopia  \

#High income economies
# Andorra, Greece, Macau SAR, Taiwan, Hong Kong, China

# Economy based on 
# 
#  tourism             Andorra",
# service, manufacturing   = "Argentina", 
# service = "Australia", 
# service =  "Bangladesh", 
# mining =  "BOL" = "Bolivia", 
# mining             "BRA" = "Brazil", 
# industry              "CHL" = "Chile", 
# manufacturing, exports  "CHN" = "China", 
# manufacturing              "COL" = "Colombia", 
# tourism   "CYP" = "Cyprus", 
# manufacturing    "ECU" = "Ecuador", 
# agriculture              "EGY" = "Egypt", 
# agriculture             "ETH" = "Ethipoia",
# exports "DEU" = "Germany",
#  agriculture      "GRC" = "Greece", 
#  agriculture             "GTM" = "Guatemala", 
#  finance             "HKG" = "Hong Kong SAR", 
#  manufacturing             "IDN" = "Indonesia", 
#  oil             "IRN" ="Iran", 
#  oil             "IRQ" = "Iraq", 
# manufacturing              "JPN" = "Japan", 
# manufacturing              "JOR" = "Jordan", 
# oil             "KAZ" = "Kazakhstan", 
# manufacturing              "KGZ" = "Kyrgyzstan", 
# service              "LBN" = "Lebanon",
# tourism              "MAC" = "Macau.SAR", 
# manufacturing              "MYS" = "Malaysia",
# manufacturing                "MEX" = "Mexico", 
# agriculture              "MMR" = "Myanmar", 
# agriculture              "NZL" = "New Zealand", 
# agriculture              "NIC" = "Nicargua", 
# petroleum              "NGA" = "Nigeria", 
# agriculture              "PAK" = "Pakistan", 
# ----manufacturing               "PER" = "Peru", 
# agriculture               "PHL" = "Philippines", 
# manufacturing              "PRI" = "Puerto.Rico", 
# trade               "ROU" = "Romania", 
# oil              "RUS" = "Russia", 
# manufacturing              "SRB" = "Serbia", 
# manufacturing              "KOR" = "South.Korea", 
# manufacturing               "TWN" = "Taiwan ROC", 
#               "TJK" = "Tajikistan", 
# manufacturing              "THA" = "Thailand", 
# agriculture              "TUN" = "Tunisia", 
# manufacturing              "TUR" = "Turkey", 
# manufacturing              "UKR" = "Ukraine", 
# consumer spending              "USA" = "United States", 
# socialist, ag+ind              "VNM" = "Vietnam",
#               "ZWE" = "Zimbabwe"
```

# Heirarchical clustering
```{r}
remotes::install_github("fivethirtyeightdata/fivethirtyeightdata")
install.packages("hclust")
library(stats)
hc.data = clean.data %>%
  filter(country %in% c("United Sates","Jordan")) %>% 
  select(q106, q107r, q108, q109r) %>% 
  drop_na() %>% 
  scale()

hc.data %>% 
  is.na() %>% 
  table()

dist(hc.data, method = "euclidean") %>% 
  head()
hc.data<- as.dist(hc.data)
hclust(hc.data, method = "ward.D")%>% 
  head()
  
```


# Unused chunks
```{r, unused_chunks, include=TRUE, echo=FALSE, eval=FALSE}


 eco_val.data %>%
  filter(q111 %in% c("1", "2")) %>% 
  rowwise() %>% 
  mutate(capitalism = sum(q106, q107r, q108, q109r, q111)) %>%
  select(country, capitalism, rel.denom) %>%   
  group_by(rel.denom) %>% 
  summarise(M.Cap = mean(capitalism))


data %>% 
  mutate(country = factor(b_country_alpha),
         rel.denom = factor(q289cs9)) %>% 
  select(country, rel.denom) %>% 

  count() %>% 
  mutate() %>% 
  ggplot(aes(x = b_country_alpha))+
  geom_bar()

  table()

a_year = factor(a_year)

head()

filter(country %in% c("CHN","IRN","USA","DEU", "IRQ","EGY","KOR" ))


f = data %>% 
   mutate(b_country_alpha = factor(b_country_alpha),
         a_year = factor(a_year)) %>% 
  filter(a_year %in% c("2020"))

levels(factor(f$b_country_alpha))



capitalism.d%>%   #getting all the means
  group_by(country) %>% 
  summarise(M.Cap = mean(capitalism))


# figure out the deal with list for pivot_wider
df = capitalism.d %>%
     drop_na() %>% 
     rownames_to_column() %>% 
     pivot_wider(names_from = "country", values_from = "capitalism") %>%      as_tibble()

View(df)
df2 = df %>% 
  dplyr::select(AND:ZWE)


```


# Thoughts
  - CHALLENGES:
     - Can't get the for loop right
     - How to deal with large datasets (I mostly deal with large number of variables and sample sizes in my work)
     - How to think of vidualizations for so many countries
     
  - LONG TERM GOAL:
     - Try ans answer research questions like how are religious values associated with attitudes towards homosesuality. 
     - Gain an understanding of how people are studying values, most of the work so far (about 80%, which is quite a but I guess), is based on this source of data.
     - I intend to work on this project in a way wherein I can use this work as something which could potentially go on my website
  


# Try tables

```{r}

library(reactable)
library(htmltools)

forecasts <- import(here("data", "wwc_forecasts.csv"),setclass = "tb_df") %>% 
  characterize() %>% 
  clean_names()

View(forecasts)

rating_cols <- c("spi", "global_o", "global_d")
group_cols <- c("group_1", "group_2", "group_3")
knockout_cols <- c("make_round_of_16", "make_quarters", "make_semis", "make_final", "win_league")
forecasts <- forecasts[, c("team", "points", "group", rating_cols, group_cols, knockout_cols)]

rating_column <- function(maxWidth = 55, ...) {
  colDef(maxWidth = maxWidth, align = "center", class = "cell number", ...)
}

group_column <- function(class = NULL, ...) {
  colDef(cell = format_pct, maxWidth = 70, align = "center", class = paste("cell number", class), ...)
}

knockout_column <- function(maxWidth = 70, class = NULL, ...) {
  colDef(
    cell = format_pct,
    maxWidth = maxWidth,
    class = paste("cell number", class),
    style = function(value) {
      # Lighter color for <1%
      if (value < 0.01) {
        list(color = "#aaa")
      } else {
        list(color = "#111", background = knockout_pct_color(value))
      }
    },
    ...
  )
}

format_pct <- function(value) {
  if (value == 0) "  \u2013 "    # en dash for 0%
  else if (value == 1) "\u2713"  # checkmark for 100%
  else if (value < 0.01) " <1%"
  else if (value > 0.99) ">99%"
  else formatC(paste0(round(value * 100), "%"), width = 4)
}

make_color_pal <- function(colors, bias = 1) {
  get_color <- colorRamp(colors, bias = bias)
  function(x) rgb(get_color(x), maxColorValue = 255)
}

off_rating_color <- make_color_pal(c("#ff2700", "#f8fcf8", "#44ab43"), bias = 1.3)
def_rating_color <- make_color_pal(c("#ff2700", "#f8fcf8", "#44ab43"), bias = 0.6)
knockout_pct_color <- make_color_pal(c("#ffffff", "#f2fbd2", "#c9ecb4", "#93d3ab", "#35b0ab"), bias = 2)

tbl <- reactable(
  forecasts,
  pagination = FALSE,
  defaultSorted = "win_league",
  defaultSortOrder = "desc",
  defaultColGroup = colGroup(headerClass = "group-header"),
  columnGroups = list(
    colGroup(name = "Team Rating", columns = rating_cols),
    colGroup(name = "Chance of Finishing Group Stage In ...", columns = group_cols),
    colGroup(name = "Knockout Stage Chances", columns = knockout_cols)
  ),
  defaultColDef = colDef(class = "cell", headerClass = "header"),
  columns = list(
    team = colDef(
      defaultSortOrder = "asc",
      minWidth = 200,
      headerStyle = list(fontWeight = 700), 
      cell = function(value, index) {
        div(
          class = "team",
          img(class = "flag", alt = paste(value, "flag"), src = sprintf("images/%s.png", value)),
          div(class = "team-name", value),
          div(class = "record", sprintf("%s pts.", forecasts[index, "points"]))
        )
      }
    ),
    points = colDef(show = FALSE),
    group = colDef(defaultSortOrder = "asc", align = "center", maxWidth = 75,
                   class = "cell group", headerStyle = list(fontWeight = 700)),
    spi = rating_column(format = colFormat(digits = 1)),
    global_o = rating_column(
      name = "Off.",
      cell = function(value) {
        scaled <- (value - min(forecasts$global_o)) / (max(forecasts$global_o) - min(forecasts$global_o))
        color <- off_rating_color(scaled)
        value <- format(round(value, 1), nsmall = 1)
        div(class = "spi-rating", style = list(background = color), value)
      }
    ),
    global_d = rating_column(
      name = "Def.", 
      defaultSortOrder = "asc",
      cell = function(value) {
        scaled <- 1 - (value - min(forecasts$global_d)) / (max(forecasts$global_d) - min(forecasts$global_d))
        color <- def_rating_color(scaled)
        value <- format(round(value, 1), nsmall = 1)
        div(class = "spi-rating", style = list(background = color), value)
      }
    ),
    group_1 = group_column(name = "1st Place", class = "border-left"),
    group_2 = group_column(name = "2nd Place"),
    group_3 = group_column(name = "3rd Place"),
    make_round_of_16 = knockout_column(name = "Make Round of 16", class = "border-left"),
    make_quarters = knockout_column(name = "Make Qtr-Finals"),
    make_semis = knockout_column(name = "Make Semifinals", maxWidth = 90),
    make_final = knockout_column(name = "Make Final"),
    win_league = knockout_column(name = "Win World Cup")
  ),
  # Emphasize borders between groups when sorting by group
  rowClass = JS("
    function(rowInfo, state) {
      const firstSorted = state.sorted[0]
      if (firstSorted && firstSorted.id === 'group') {
        const nextRow = state.pageRows[rowInfo.viewIndex + 1]
        if (nextRow && rowInfo.row.group !== nextRow.group) {
          return 'group-last'
        }
      }
    }"
  ),
  showSortIcon = FALSE,
  borderless = TRUE,
  class = "standings-table"
)

div(class = "standings",
  div(class = "title",
    h2("2019 Women's World Cup Predictions"),
    "Soccer Power Index (SPI) ratings and chances of advancing for every team"
  ),
  tbl,
  "Forecast from before 3rd group matches"
)
```

# My tables effort

```{r}
library(reactable)
#Country with sex - 1= Male , 2= Female

table.data =  clean.data %>% 
  select(country, q260) %>% 
  mutate(q260 = recode(q260,
         `1` ="Male",
         `2` = "Female")) %>% 
  as_tibble() %>% 
  rename(Sex = q260,
         Country = country) %>% 
  group_by(Country) %>%
  count(Sex) %>% 
  pivot_wider(names_from = Sex, values_from = n) %>% 
  rowwise() %>%   
  mutate(Female.perc = Female/sum(Female, Male),
         Male.perc = Male/sum(Male, Female)) %>% 
  select(Country, Female.perc, Male.perc) 
    
reactable(table.data) 
library(htmltools)


# Render a bar chart with a label on the left
bar_chart <- function(label, width = "100%", height = "14px", fill = "#00bfc4", background = NULL) {
    bar <- div(style = list(background = fill, width = width, height = height))
    chart <- div(style = list(flexGrow = 1, marginLeft = "6px", background = background), bar)
   div(style = list(display = "flex", alignItems = "center"), label, chart)
}


reactable(
  table.data,
  defaultSorted = "Country",
  columns = list(
    #Col1
    Country = colDef(
      name = "Country",
      format = colFormat(prefix = "#"),
      defaultSortOrder = "asc",
      minWidth = 200
      
    ),
    #Col2
    Female.perc = colDef(
      name = "Female",
      defaultSortOrder = "desc",
      # Render the bar charts using a custom cell render function
      cell = function(value) {
        # Format as percentages with 1 decimal place
        value <- paste0(format(value * 100, nsmall = 1), "%")
        bar_chart(value, width = value, fill = "#7fcdbb", background = "#e1e1e1")
      },
      # And left-align the columns
      align = "left",
       format = colFormat(digits = 1)
    ),
    #Col3
    Male.perc = colDef(
      name = "Male",
      defaultSortOrder = "desc",
       # Render the bar charts using a custom cell render function
      cell = function(value) {
        # Format as percentages with 1 decimal place
        value <- paste0(format(value * 100, nsmall = 1), "%")
        bar_chart(value, width = value, fill = "#2c7fb8", background = "#e1e1e1")
      },
      # And left-align the columns
      align = "left"
    )
  ),

  theme = reactableTheme(
    borderColor = "#ece2f0",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(
      fontFamily = "sans-serif"
    ),
    searchInputStyle = list(width = "10%")
  )
)




```

